MLExplain

### 2018-05-24 paper.tex
Rebougé la figure et continué sur MLExplain
j'avais pas compris que la figure présentait MLExplain et non JSExplain.

% J'aime pas trop la voir tout en bas, mais ici ça fait bizarre, si tu as mieux
% je prends.

@@

\subsubsection{fOCaml}
This compiler does not recognized the whole OCaml language, it can only handle
a small subset we named \texttt{fOCaml}. Among other restrictions, it cannot
handle objects and imperative features, exceptions, inner modules, and tuples.

>>>>

Modes \texttt{unlog} and \texttt{log} exist so that auxiliary code in the
interpreter -- like linked-list or hash-map internal-management functions -- is
not traced.  The user is thus able to concentrate on the logical part of the
interpreter functioning and forget about implementation details.

\subsubsection{fOCaml}
This compiler does not recognized the whole OCaml language, it can only handle
a small subset we named \texttt{fOCaml}. Among other restrictions, it cannot
handle objects and imperative features, exceptions, inner modules, and tuples.
The main reason for this limitation is that compiling OCaml into JavaScript is
not trivial, many features -- e.g. nested pattern matching -- are hard to
represent to JavaScript.

The fOCaml code is compiled into \texttt{fJs}, a functional subset of
JavaScript. The compiler preserves as much as possible the code structure to
enable the user to understand both fOCaml and fJs codes as the same one.

% Petite explication sur le fait que du coup on écrit du code fonctionnel pur
% et les implications que ça a ?

\section{MLExplain}

At first glance, JSExplain seems tightly linked to JavaScript. However, the
architecture of the project actually allows us to take off the interpreter
completely and replace it with another one.

% Plus de blabla

\subsection{Two compilers}

To interpret OCaml code, we need to parse it. However, our compiler does not
allow us to use the standard library nor an external one.

@@
